Model

### 2019-10-15 stats/model.Rmd
add sampler to save memory

@@

@@

var header = "iteration,a,b,c,d,e,f"
var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);

>>>>

  query.add(["pragmaticModelPredictions","parameterFree", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

@@

  query.add(["pragmaticModelPredictions","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])

@@

var header = "iteration,a,b,c,d,e,f,g,h"
var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);
